Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

With global garbage collection, the cost of scanning entire heap often is very expensive. To reduce the high price for global scanning of the heap, garbage collection is initiated when the threshold is met. Promptness property helps to keep heap memory free of floating garbage instantly. This property helps to avoid global scanning and also easy availability of free memory for allocation.

@@

Safety property is the most crucial part of the garbage collection which is directly related to advantages of using garbage collection. This avoids any dangling pointers and double free bugs. The property guarantees that every garbage collector will delete only garbage object. While most garbage collector in literature satisfies this property, there are some that cannot satisfy this property. This thesis requires garbage collector to be safety in the multi-collector environment which is challenging given that there is no global synchronization. In distributed memory system, the property is very difficult to satisfy as the garbage collector cannot get the global snapshot of a heap at any point in time. Locality based algorithm works only by using information obtained from neighbors. Evaluating a global predicate using local information is challenging by all means. This thesis guarantees the safety of collectors designed for both environments.

@@

Completeness helps garbage collector to claim that it collects all garbage objects in the heap, thereby no memory leaks in the heap . Reference counting garbage collector is well known for incomplete garbage collection due to their inability to collect cyclic garbage. This property is challenging as the locality based collectors usually use reference counting. Garbage collector with localized decision-making guarantee completeness is necessary to make the collector highly adaptable to enhance the performance of the applications. Collectors designed for both environments uses reference counting based technique to solve the problem and guarantees the garbage collectors are complete.

>>>>

With global garbage collection, the cost of scanning entire heap often is very expensive. To reduce the high price for global scanning of the heap, garbage collection is initiated when the threshold is met. The promptness property helps to keep heap memory free of floating garbage in a timely manner. This property helps to avoid global scanning and also quick availability of free memory for allocation.

@@

The safety property is the most crucial part of garbage collection. This avoids any dangling pointers and double free bugs. The property guarantees that every garbage collector will delete only garbage objects. While most garbage collector in literature satisfies this property, there are some that cannot satisfy this property. This thesis requires garbage collector to be safe in the multi-collector environment which is challenging given that there is no global synchronization. In a distributed memory system, this property is very difficult to satisfy as the garbage collector cannot get the global snapshot of a heap at any point in time. A locality-based algorithm works by using information obtained only from neighbors. Evaluating a global predicate using local information is challenging by all means. This thesis guarantees the safety of collectors designed for both environments.

@@

Completeness guarantees that a garbage collector will collect all garbage objects in the heap, thereby removing all memory leaks in the heap. Reference counting garbage collectors are well known for incomplete garbage collection due to their inability to collect cyclic garbage. This property is challenging as the locality-based collectors usually use reference counting. Collectors designed for both environments use reference counting and tracing echnique to solve the problem and guarantees the garbage collectors are complete.
